GPU-friendly Stroke Expansion

### 2024-04-29 paper.tex
fix keywords; inline comment

@@

Using a subpixel Fréchet distance bound guarantees that the rendered image does not deviate visibly from the exact rendering. Another choice would be uniform steps in tangent angle, as chosen by polar stroking\cite{Kilgard2020}. However, at small curvature, the stroked path can be off by several pixels, and at large curvature there may be considerably more subdivision than needed for faithful rendering. It should be noted, to avoid the undershoot at low curvature, both the Skia\cite{Skia} and Rive\cite{Rive} renderers use a hybrid of the Wang and polar stroking error metrics.

Proposed image: show circular arcs with polar stroking vs near-optimal flattening.

@@

\begin{itemize}
    \item The GPU implementation sequentializes some work that could be parallel, and is thus not as well load-balanced as it might be. An appealing future direction is to split the pipeline into separate stages, executed by the GPU as nodes in a work graph\cite{Patel2024}. This structure is appealing because load balancing is done by hardware.

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

>>>>

\keywords{Vector Graphics, Stroke, Offset Curve, Path Rendering, GPU}

@@

Using a subpixel Fréchet distance bound guarantees that the rendered image does not deviate visibly from the exact rendering. Another choice would be uniform steps in tangent angle, as chosen by polar stroking[\citenum{Kilgard2020}]. However, at small curvature, the stroked path can be off by several pixels, and at large curvature there may be considerably more subdivision than needed for faithful rendering. It should be noted, to avoid the undershoot at low curvature, both the Skia[\citenum{Skia}] and Rive[\citenum{Rive}] renderers use a hybrid of the Wang and polar stroking error metrics.

TODO: Proposed image: show circular arcs with polar stroking vs near-optimal flattening.

@@

\begin{itemize}
    \item The GPU implementation sequentializes some work that could be parallel, and is thus not as well load-balanced as it might be. An appealing future direction is to split the pipeline into separate stages, executed by the GPU as nodes in a work graph[\citenum{Patel2024}]. This structure is appealing because load balancing is done by hardware.

@@

\bibliographystyle{ACM-Reference-Format}
\setcitestyle{numbers} % Switch back to numerical mode to show citation numbers in bibliography
\bibliography{paper}
